Revealing transient strain in geodetic data with Gaussian process regression

### 2017-09-24 RevisedSubmission/hines_hetland_2017_gji.tex
did more

\mu_{\hat{u}_i}(p) = C_{u_i}(p,\mitbf{P})\left(\mitbf{\Sigma} + \kappa^2\mitbf{G}\mitbf{G}^T\right)^{-1}\mitbf{d}_*

@@

                         \mitbf{d}_* \\

@@

Now that we have a posterior estimate of transient displacements, we can write the components of $\dot\varepsilon$ as 
\begin{equation}\label{eq:StrainRate}
\dot\varepsilon_{ij}(p) = \frac{1}{2} \frac{\partial}{\partial t} \left(
                                        \frac{\partial \hat{u}_i(p)}{\partial x_j} +  
                                        \frac{\partial \hat{u}_j(p)}{\partial x_i}\right).
\end{equation}
The transient strain rate components are stochastic processes whose distributions can be interpreted as the distributions of samples of $\hat{u}$ that have been differentiated by the operator from eq. (\ref{eq:StrainRate}). Since differentiation is a linear operation, the transient strain rate components are Gaussian processes. From \citet[sec. 10.2]{Papoulis1991}, we find that the components of $\dot{\varepsilon}$ have mean functions
\begin{equation}\label{eq:StrainMean}
\mu_{\dot\varepsilon_{ij}}(p) = \frac{1}{2}\frac{\partial}{\partial t}\left(
                                  \frac{\partial \mu_{\hat{u}_i}(p)}{\partial x_j} + 
                                  \frac{\partial \mu_{\hat{u}_j}(p)}{\partial x_i} \right)
\end{equation} 
and covariance functions
\begin{equation}\label{eq:StrainCov}
C_{\dot\varepsilon_{ij}}(p,p') = \frac{1}{4} \frac{\partial^2}{\partial t \, \partial t'}\left(
                                   \frac{\partial^2 C_{\hat{u}_i}(p,p')}{\partial x_j \, \partial x'_j} + 
                                   \frac{\partial^2 C_{\hat{u}_j}(p,p')}{\partial x_i \, \partial x'_i} \right).
\end{equation}

>>>>

\mu_{\hat{u}_i}(p) = C_{u_i}(p,\mitbf{P})\left(\mitbf{\Sigma} + \kappa^2\mitbf{G}\mitbf{G}^T\right)^{-1}\mitbf{d}^*_i

@@

                         \mitbf{d}^*_i \\

@@

To ensure that the inverse matrices in eqs. (\ref{eq:PosteriorMean3}) and (\ref{eq:PosteriorCov3}) exist, each column in $\mitbf{G}$ must be linearly independent and there must be at least as many observations as basis functions ($n \geq 6m$).

Now that we have a posterior estimate of transient displacements, we can write the components of $\dot\varepsilon$ as 
\begin{equation}\label{eq:StrainRate}
\dot\varepsilon_{ij}(p) = \frac{1}{2} \frac{\partial}{\partial t} \left(
                                        \frac{\partial \hat{u}_i(p)}{\partial x_j} +  
                                        \frac{\partial \hat{u}_j(p)}{\partial x_i}\right).
\end{equation}
The components of $\dot\varepsilon$ are stochastic processes that are obtained from differentiating, adding, and scaling the Gaussian processes $\hat{u}_\mathrm{e}$ and $\hat{u}_\mathrm{n}$. To give a more intuitive interpretation of $\dot\varepsilon_{ij}$, we can consider realizations of $\dot{\varepsilon}_{ij}$ to be realizations of $\hat{u}_i$ and $\hat{u}_j$ that have undergone the operations from eq. (\ref{eq:StrainRate}). Since the operations from eq. (\ref{eq:StrainRate}) are linear, we know that $\dot\varepsilon_{ij}$ is also a Gaussian process. From \citet[sec. 10.2]{Papoulis1991}, we find that $\dot{\varepsilon}_{ij}$ has a mean function
\begin{equation}\label{eq:StrainMean}
\mu_{\dot\varepsilon_{ij}}(p) = \frac{1}{2}\frac{\partial}{\partial t}\left(
                                  \frac{\partial \mu_{\hat{u}_i}(p)}{\partial x_j} + 
                                  \frac{\partial \mu_{\hat{u}_j}(p)}{\partial x_i} \right)
\end{equation} 
and covariance function
\begin{equation}\label{eq:StrainCov}
C_{\dot\varepsilon_{ij}}(p,p') = \frac{1}{4} \frac{\partial^2}{\partial t \, \partial t'}\left(
                                   \frac{\partial^2 C_{\hat{u}_i}(p,p')}{\partial x_j \, \partial x'_j} + 
                                   \frac{\partial^2 C_{\hat{u}_j}(p,p')}{\partial x_i \, \partial x'_i} \right).
\end{equation}
